Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-03-03 manuscript.Rmd
more intro citations

Measuring infant movement with inertial movement units (IMUs) is a promising avenue for long form recordings of motor behavior in the home. Lightweight sensors (10-30 g) can be embedded in garments to make recordings fully *mobile*, and they are *unobtrusive* because they do not require a researcher's presence nor do they record sensitive audio/video that might influence participants' behavior [(Cliff et al., 2009; de Barbaro, 2019; Lobo et al., 2019; Bruijns et al., 2020)]. Many commercially-available and inexpensive IMUs have > 12 hour battery life with onboard storage to record *real-time*, *full-day* motion data at a sampling rate that is higher than typical video (e.g., 50-100 Hz). Moreover, past work has successfully recorded the rate of leg kicks [e.g., @DengTrujillo-Priego2019] and activity intensity [@SchnellerBentsen2017] in infants and children across multiple days. 
<!-- CHECK THAT CITATIONS ARE FULL DAY -->

The open question is whether *automatic classification* is sufficiently accurate to measure movement categories that are relevant to developmental and clinical research, and whether measurement validity is acceptable over long recording periods. IMUs typically contain accelerometers that measure linear acceleration paired with gyroscopes that measure angular acceleration. Unlike motion tracking systems that might be used in a lab, IMUs do not provide data about the position of the body in space. Thus, data processing algorithms are needed to classify the raw sensor data (i.e., linear and angular acceleration timeseries) into meaningful categories (e.g., supine, prone, sitting, upright). The difficulty of the classification task depends on the categories of interest. More basic aspects of movement, such as overall activity intensity, can be identified by taking the magnitude of acceleration (irrespective of direction) and applying thresholds or cut-points to define when a movement has occurred at a particular intensity [(Trost et al., 2012; Kuzik et al., 2015; Hager et al., 2017; Armstrong et al., 2019)].

Categorizing body position---supine on the back, prone on the belly, sitting, upright, or held off the ground by a caregiver---is too complex for cut-point definitions to be accurate. First, the magnitude of movement can vary greatly *within* a body position. An upright infant can be standing still or can be walking briskly across the room. A prone infant and be stationary in "tummy time" or crawling in myriad ways [ADOLPH]. Moreover, the configuration of the arms, legs, and torso within a body position can vary greatly in everyday contexts. Infants can sit on the floor in a tripod position with support from an arm, in a "V" position with legs fully extended, in a "W" position with knees bent. Sitting on a caregivers' lap without the need to maintain balance means that the legs can dangle and the torso can lean in different directions. Sitting in a high chair or car seat reduces the magnitude of postural sway within sitting, and creates even more possibilities for how the arms and legs may move relative to the torso. Indeed, creating an all-encompassing set of rules for how to annotate sitting from video is no trivial task because of the various ways that sitting can occur in daily life. Finally, caregivers frequently pick up and transport infants, creating motion signals that need to be differentiated from independent activity [@KwonZavos2019; @PatelShi2019]. Thus, modern approaches to human activity recognition have used machine learning to classify activity categories based on features derived from IMU data in adults [(Preece et al., 2009; Arif and Kattan, 2015)], children [(Nam and Park, 2013; Zhao et al., 2013; Ren et al., 2016; Stewart et al., 2018)], and infants [Franchak; Airaksinen; Yao]. Synchronized video with ground-truth human annotations creates training data for a machine learning algorithm, such as a random forest model, that can be later used to predict categories from IMU data that was not annotated. Crucially, this allows automatic classification to scale to full day recording by relying on a relatively smaller set of video annotation. 
GREENSPAN...

Three prior investigations have used machine learning to categorize infant body position from IMUs towards the goal of collecting full-day data. @AiraksinenRasanen2020 tested 4- to 8-month-olds in a laboratory visit, and found XX% accuracy (kappa = XX%) in distinguishing between body position categories that crawling infants could perform on the floor (excluding times that infants were held by caregivers). Using a wider age range of XX-XX, [FRANCHAK] found XX% accuracy (kappa = XX%) in a laboratory validation study in categorizing body position that included infants who could both crawl and walk and also categorized caregiver holding. Most recently, [Airaksinen NEW] conducted a validation study of body position classification in either a home or clinic testing in 4- to 19-month-olds, refining their previous method to detect moments that infants were carried by caregivers. Classification accuracy did not vary between lab and home settings, and was generally high (95%, kappa = .93). Although all three studies yielded promising classification accuracy, accuracy was assessed in brief (15-60 minute) sessions supervised by a researcher, leaving the open question of how well body position classification will scale to testing across an entire day of natural home life. 
YAO?

@@

Accordingly, the overarching goal of the current study is to test the feasibility and validity of long-form body position recording in the home during unsupervised, everyday behavior. Supervised recordings from past work [CITES], whether in the home or in the lab, let researchers set up the situation to encourage or restrict certain behaviors. Usually, caregivers are asked to play with the infant. However, across a real day, non-play activities (e.g., eating lunch in a high chair) create challenging situations for applying automated classification of body position. Will models trained on video-recorded observations at the beginning of the day generalize to predict behavior at a later time? Assessing the validity of temporally *distal* periods is a crucial step to establish whether automatic classification can be used to measure body position across a day.

In the current study, we report the feasibility and validity of body position classification over the full day in the home based on 35 testing sessions from XX infants aged 4-14 months. Participants received a custom pair of infant leggings embedded with 4 IMUs (one on each ankle and one on each hip) and a video camera to collect ground truth data about infant body position. A *proximal comparison* period began when participants received the equipment and completed a guided phone call during which caregivers were asked to elicit different body positions based on prompts from the experimenter. Although not directly supervised, this period was most similar to previous recordings because it occurred during a convenient time for the infant and caregiver to play while they received instructions from the experimenter. The **first goal** of the current study was to determine the accuracy of body position classification during the proximal comparison period using this novel, semi-supervised procedure in participants' homes.

@@

After this second video recording period, we asked caregivers to keep infants wearing IMUs for the rest of the day until their regular bedtime, creating the **first real-time, full-day dataset of infant body position**. Interpreting such data required caregivers to log when infants napped, when they removed the sensor garment for diaper changes or other reasons, and when infants went to bed at the end of the day. The **third goal** of the study was to examine the quality of the full-day data. Could body position be successfully recorded over the desired period? Finally, the novel full-day dataset affords us a unique chance to ask whether the estimated time infants spent in different body positions align with past results using video and survey methods. Thus, the **fourth goal** of the current study was to determine whether full-day body position measurements conformed to expectations about age differences in body position. Based on past results [CITE], infants should spend increasingly more time sitting and upright but less time supine over the age range tested (4 to 14 months).

>>>>

Measuring infant movement with inertial movement units (IMUs) is a promising avenue for long form recordings of motor behavior in the home [@CliffReilly2009; @Barbaro2019; @BruijnsTruelove2020; @LoboHall2019]. Lightweight sensors (10-30 g) can be embedded in garments to make recordings fully *mobile*, and they are *unobtrusive* because they do not require a researcher's presence nor do they record sensitive audio/video that might influence participants' behavior. Many commercially-available and inexpensive IMUs have > 12 hour battery life with onboard storage to record *real-time*, *full-day* motion data at a sampling rate that is higher than typical video (e.g., 50-100 Hz). Moreover, past work has successfully recorded the rate of leg kicks [e.g., @DengTrujillo-Priego2019] and activity intensity [@SchnellerBentsen2017] in infants and children across multiple days.

The open question is whether *automatic classification* is sufficiently accurate to measure movement categories that are relevant to developmental and clinical research, and whether measurement validity is acceptable over long recording periods. IMUs typically contain accelerometers that measure linear acceleration paired with gyroscopes that measure angular acceleration. Unlike motion tracking systems that might be used in a lab, IMUs do not provide data about the position of the body in space. Thus, data processing algorithms are needed to classify the raw sensor data (i.e., linear and angular acceleration timeseries) into meaningful categories (e.g., supine, prone, sitting, upright). The difficulty of the classification task depends on the categories of interest. More basic aspects of movement, such as overall activity intensity, can be identified by taking the magnitude of acceleration (irrespective of direction) and applying thresholds or cut-points to define when a movement has occurred at a particular intensity [e.g., @HagerTilton2017; @ArmstrongCovington2019].

Categorizing body position---supine on the back, prone on the belly, sitting, upright, or held off the ground by a caregiver---is too complex for cut-point definitions to be accurate. First, the magnitude of movement can vary greatly *within* a body position. An upright infant can be standing still or can be walking briskly across the room. A prone infant and be stationary in "tummy time", or they can crawl in myriad ways [@AdolphVereijken1998]. Moreover, the configuration of the arms, legs, and torso within a body position can vary greatly in everyday contexts. Infants can sit on the floor in a tripod position with support from an arm, in a "V" position with legs fully extended, in a "W" position with knees bent. Sitting on a caregivers' lap without the need to maintain balance means that the legs can dangle and the torso can lean in different directions. Sitting in a high chair or car seat reduces the magnitude of postural sway within sitting, and creates even more possibilities for how the arms and legs may move relative to the torso. Indeed, creating an all-encompassing set of rules for how to annotate sitting from video is no trivial task because of the various ways that sitting can occur in daily life. Finally, caregivers frequently pick up and transport infants, creating motion signals that need to be differentiated from independent activity [@KwonZavos2019; @PatelShi2019]. Thus, modern approaches to human activity recognition have used machine learning to classify activity categories based on features derived from IMU data in adults [@Preece2009; @Arif2015], children [@NamPark2013; @RenDing2016; @StewartNarayanan2018], and infants [@YaoPlotz2019; @FranchakScott2021; @AiraksinenRasanen2020]. Synchronized video with ground-truth human annotations creates training data for a machine learning algorithm, such as a random forest model, that can be later used to predict categories from IMU data that was not annotated. Crucially, this allows automatic classification to scale to full day recording by relying on a relatively smaller set of video annotation.

<!-- NEED TO FIT IN GREENSPAN posture from cut points, Hewitt Tummy time, Yao holding-->

Three prior investigations have used machine learning to categorize infant body position from IMUs towards the goal of collecting full-day data. @AiraksinenRasanen2020 tested 4- to 8-month-olds in a laboratory visit, and found 95% accuracy in distinguishing between body position categories that crawling infants could perform on the floor (excluding times that infants were held by caregivers). Using a wider age range of 6-18 months, @FranchakScott2021 found 98% accuracy (*kappa* = 95%) in a laboratory validation study in categorizing body position that included infants who could both crawl and walk and also included a category for caregiver holding. Most recently, @AiraksinenGallen2022 conducted a validation study of body position classification in either a home or clinic testing in 4- to 19-month-olds, refining their previous method to detect moments that infants were carried by caregivers. Classification accuracy did not vary between lab and home settings, and was generally high (95%, *kappa* = .93). Although all three studies yielded promising classification accuracy, accuracy was assessed in brief (15-60 minute) sessions supervised by a researcher, leaving the open question of how well body position classification will scale to testing across an entire day of natural home life.

<!-- Could have a bit more detail in this last paragraph -->

@@

Accordingly, the overarching goal of the current study is to test the feasibility and validity of long-form body position recording in the home during unsupervised, everyday behavior. Supervised recordings from past work [@FranchakScott2021; @AiraksinenRasanen2020; @AiraksinenGallen2022], whether in the home or in the lab, let researchers set up the situation to encourage or restrict certain behaviors. Usually, caregivers are asked to play with the infant. However, across a real day, non-play activities (e.g., eating lunch in a high chair) create challenging situations for applying automated classification of body position. Will models trained on video-recorded observations at the beginning of the day generalize to predict behavior at a later time? Assessing the validity of temporally *distal* periods is a crucial step to establish whether automatic classification can be used to measure body position across a day.

In the current study, we report the feasibility and validity of body position classification over the full day in the home based on 35 testing sessions from 23 infants aged 4-14 months. Participants received a custom pair of infant leggings embedded with 4 IMUs (one on each ankle and one on each hip) and a video camera to collect ground truth data about infant body position. A *proximal comparison* period began when participants received the equipment and completed a guided phone call during which caregivers were asked to elicit different body positions based on prompts from the experimenter. Although not directly supervised, this period was most similar to previous recordings because it occurred during a convenient time for the infant and caregiver to play while they received instructions from the experimenter. The **first goal** of the current study was to determine the accuracy of body position classification during the proximal comparison period using this novel, semi-supervised procedure in participants' homes.

@@

After this second video recording period, we asked caregivers to keep infants wearing IMUs for the rest of the day until their regular bedtime, creating the **first real-time, full-day dataset of infant body position**. Interpreting such data required caregivers to log when infants napped, when they removed the sensor garment for diaper changes or other reasons, and when infants went to bed at the end of the day. The **third goal** of the study was to examine the quality of the full-day data. Could body position be successfully recorded over the desired period? Finally, the novel full-day dataset affords us a unique chance to ask whether the estimated time infants spent in different body positions align with past results using video and survey methods. Thus, the **fourth goal** of the current study was to determine whether full-day body position measurements conformed to expectations about age differences in body position. Based on past results [@Survey], infants should spend increasingly more time sitting and upright but less time supine over the age range tested (4 to 14 months).

### 2023-03-03 manuscript.tex
more intro citations

Measuring infant movement with inertial movement units (IMUs) is a promising avenue for long form recordings of motor behavior in the home. Lightweight sensors (10-30 g) can be embedded in garments to make recordings fully \emph{mobile}, and they are \emph{unobtrusive} because they do not require a researcher's presence nor do they record sensitive audio/video that might influence participants' behavior {[}(Cliff et al., 2009; de Barbaro, 2019; Lobo et al., 2019; Bruijns et al., 2020){]}. Many commercially-available and inexpensive IMUs have \textgreater{} 12 hour battery life with onboard storage to record \emph{real-time}, \emph{full-day} motion data at a sampling rate that is higher than typical video (e.g., 50-100 Hz). Moreover, past work has successfully recorded the rate of leg kicks (e.g., Deng et al., 2019) and activity intensity (SCHNELLER et al., 2017) in infants and children across multiple days.

The open question is whether \emph{automatic classification} is sufficiently accurate to measure movement categories that are relevant to developmental and clinical research, and whether measurement validity is acceptable over long recording periods. IMUs typically contain accelerometers that measure linear acceleration paired with gyroscopes that measure angular acceleration. Unlike motion tracking systems that might be used in a lab, IMUs do not provide data about the position of the body in space. Thus, data processing algorithms are needed to classify the raw sensor data (i.e., linear and angular acceleration timeseries) into meaningful categories (e.g., supine, prone, sitting, upright). The difficulty of the classification task depends on the categories of interest. More basic aspects of movement, such as overall activity intensity, can be identified by taking the magnitude of acceleration (irrespective of direction) and applying thresholds or cut-points to define when a movement has occurred at a particular intensity {[}(Trost et al., 2012; Kuzik et al., 2015; Hager et al., 2017; Armstrong et al., 2019){]}.

Categorizing body position---supine on the back, prone on the belly, sitting, upright, or held off the ground by a caregiver---is too complex for cut-point definitions to be accurate. First, the magnitude of movement can vary greatly \emph{within} a body position. An upright infant can be standing still or can be walking briskly across the room. A prone infant and be stationary in ``tummy time'' or crawling in myriad ways {[}ADOLPH{]}. Moreover, the configuration of the arms, legs, and torso within a body position can vary greatly in everyday contexts. Infants can sit on the floor in a tripod position with support from an arm, in a ``V'' position with legs fully extended, in a ``W'' position with knees bent. Sitting on a caregivers' lap without the need to maintain balance means that the legs can dangle and the torso can lean in different directions. Sitting in a high chair or car seat reduces the magnitude of postural sway within sitting, and creates even more possibilities for how the arms and legs may move relative to the torso. Indeed, creating an all-encompassing set of rules for how to annotate sitting from video is no trivial task because of the various ways that sitting can occur in daily life. Finally, caregivers frequently pick up and transport infants, creating motion signals that need to be differentiated from independent activity (Kwon et al., 2019; Patel et al., 2019). Thus, modern approaches to human activity recognition have used machine learning to classify activity categories based on features derived from IMU data in adults {[}(Preece et al., 2009; Arif and Kattan, 2015){]}, children {[}(Nam and Park, 2013; Zhao et al., 2013; Ren et al., 2016; Stewart et al., 2018){]}, and infants {[}Franchak; Airaksinen; Yao{]}. Synchronized video with ground-truth human annotations creates training data for a machine learning algorithm, such as a random forest model, that can be later used to predict categories from IMU data that was not annotated. Crucially, this allows automatic classification to scale to full day recording by relying on a relatively smaller set of video annotation.
GREENSPAN\ldots{}

Three prior investigations have used machine learning to categorize infant body position from IMUs towards the goal of collecting full-day data. Airaksinen et al. (2020) tested 4- to 8-month-olds in a laboratory visit, and found XX\% accuracy (kappa = XX\%) in distinguishing between body position categories that crawling infants could perform on the floor (excluding times that infants were held by caregivers). Using a wider age range of XX-XX, {[}FRANCHAK{]} found XX\% accuracy (kappa = XX\%) in a laboratory validation study in categorizing body position that included infants who could both crawl and walk and also categorized caregiver holding. Most recently, {[}Airaksinen NEW{]} conducted a validation study of body position classification in either a home or clinic testing in 4- to 19-month-olds, refining their previous method to detect moments that infants were carried by caregivers. Classification accuracy did not vary between lab and home settings, and was generally high (95\%, kappa = .93). Although all three studies yielded promising classification accuracy, accuracy was assessed in brief (15-60 minute) sessions supervised by a researcher, leaving the open question of how well body position classification will scale to testing across an entire day of natural home life.
YAO?

@@

Accordingly, the overarching goal of the current study is to test the feasibility and validity of long-form body position recording in the home during unsupervised, everyday behavior. Supervised recordings from past work {[}CITES{]}, whether in the home or in the lab, let researchers set up the situation to encourage or restrict certain behaviors. Usually, caregivers are asked to play with the infant. However, across a real day, non-play activities (e.g., eating lunch in a high chair) create challenging situations for applying automated classification of body position. Will models trained on video-recorded observations at the beginning of the day generalize to predict behavior at a later time? Assessing the validity of temporally \emph{distal} periods is a crucial step to establish whether automatic classification can be used to measure body position across a day.

In the current study, we report the feasibility and validity of body position classification over the full day in the home based on 35 testing sessions from XX infants aged 4-14 months. Participants received a custom pair of infant leggings embedded with 4 IMUs (one on each ankle and one on each hip) and a video camera to collect ground truth data about infant body position. A \emph{proximal comparison} period began when participants received the equipment and completed a guided phone call during which caregivers were asked to elicit different body positions based on prompts from the experimenter. Although not directly supervised, this period was most similar to previous recordings because it occurred during a convenient time for the infant and caregiver to play while they received instructions from the experimenter. The \textbf{first goal} of the current study was to determine the accuracy of body position classification during the proximal comparison period using this novel, semi-supervised procedure in participants' homes.

@@

After this second video recording period, we asked caregivers to keep infants wearing IMUs for the rest of the day until their regular bedtime, creating the \textbf{first real-time, full-day dataset of infant body position}. Interpreting such data required caregivers to log when infants napped, when they removed the sensor garment for diaper changes or other reasons, and when infants went to bed at the end of the day. The \textbf{third goal} of the study was to examine the quality of the full-day data. Could body position be successfully recorded over the desired period? Finally, the novel full-day dataset affords us a unique chance to ask whether the estimated time infants spent in different body positions align with past results using video and survey methods. Thus, the \textbf{fourth goal} of the current study was to determine whether full-day body position measurements conformed to expectations about age differences in body position. Based on past results {[}CITE{]}, infants should spend increasingly more time sitting and upright but less time supine over the age range tested (4 to 14 months).

@@

@@

@@

@@

@@

@@

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-SchnellerBentsen2017}{}}%
SCHNELLER, M. B., BENTSEN, P., NIELSEN, G., BRØND, J. C., RIED-LARSEN, M., MYGIND, E., \& SCHIPPERIJN, J. (2017). Measuring children's physical activity. \emph{Medicine \& Science in Sports \& Exercise}, \emph{49}(6), 1261--1269. \url{https://doi.org/10.1249/mss.0000000000001222}

@@

>>>>

Measuring infant movement with inertial movement units (IMUs) is a promising avenue for long form recordings of motor behavior in the home (Barbaro, 2019; Bruijns et al., 2020; Cliff et al., 2009; Lobo et al., 2019). Lightweight sensors (10-30 g) can be embedded in garments to make recordings fully \emph{mobile}, and they are \emph{unobtrusive} because they do not require a researcher's presence nor do they record sensitive audio/video that might influence participants' behavior. Many commercially-available and inexpensive IMUs have \textgreater{} 12 hour battery life with onboard storage to record \emph{real-time}, \emph{full-day} motion data at a sampling rate that is higher than typical video (e.g., 50-100 Hz). Moreover, past work has successfully recorded the rate of leg kicks (e.g., Deng et al., 2019) and activity intensity (Schneller et al., 2017) in infants and children across multiple days.

The open question is whether \emph{automatic classification} is sufficiently accurate to measure movement categories that are relevant to developmental and clinical research, and whether measurement validity is acceptable over long recording periods. IMUs typically contain accelerometers that measure linear acceleration paired with gyroscopes that measure angular acceleration. Unlike motion tracking systems that might be used in a lab, IMUs do not provide data about the position of the body in space. Thus, data processing algorithms are needed to classify the raw sensor data (i.e., linear and angular acceleration timeseries) into meaningful categories (e.g., supine, prone, sitting, upright). The difficulty of the classification task depends on the categories of interest. More basic aspects of movement, such as overall activity intensity, can be identified by taking the magnitude of acceleration (irrespective of direction) and applying thresholds or cut-points to define when a movement has occurred at a particular intensity (Armstrong et al., 2019; e.g., Hager et al., 2017).

Categorizing body position---supine on the back, prone on the belly, sitting, upright, or held off the ground by a caregiver---is too complex for cut-point definitions to be accurate. First, the magnitude of movement can vary greatly \emph{within} a body position. An upright infant can be standing still or can be walking briskly across the room. A prone infant and be stationary in ``tummy time'', or they can crawl in myriad ways (Adolph et al., 1998). Moreover, the configuration of the arms, legs, and torso within a body position can vary greatly in everyday contexts. Infants can sit on the floor in a tripod position with support from an arm, in a ``V'' position with legs fully extended, in a ``W'' position with knees bent. Sitting on a caregivers' lap without the need to maintain balance means that the legs can dangle and the torso can lean in different directions. Sitting in a high chair or car seat reduces the magnitude of postural sway within sitting, and creates even more possibilities for how the arms and legs may move relative to the torso. Indeed, creating an all-encompassing set of rules for how to annotate sitting from video is no trivial task because of the various ways that sitting can occur in daily life. Finally, caregivers frequently pick up and transport infants, creating motion signals that need to be differentiated from independent activity (Kwon et al., 2019; Patel et al., 2019). Thus, modern approaches to human activity recognition have used machine learning to classify activity categories based on features derived from IMU data in adults (Arif \& Kattan, 2015; Preece et al., 2009), children (Nam \& Park, 2013; Ren et al., 2016; Stewart et al., 2018), and infants (Airaksinen et al., 2020; Franchak et al., 2021; Yao et al., 2019). Synchronized video with ground-truth human annotations creates training data for a machine learning algorithm, such as a random forest model, that can be later used to predict categories from IMU data that was not annotated. Crucially, this allows automatic classification to scale to full day recording by relying on a relatively smaller set of video annotation.

Three prior investigations have used machine learning to categorize infant body position from IMUs towards the goal of collecting full-day data. Airaksinen et al. (2020) tested 4- to 8-month-olds in a laboratory visit, and found 95\% accuracy in distinguishing between body position categories that crawling infants could perform on the floor (excluding times that infants were held by caregivers). Using a wider age range of 6-18 months, Franchak et al. (2021) found 98\% accuracy (\emph{kappa} = 95\%) in a laboratory validation study in categorizing body position that included infants who could both crawl and walk and also included a category for caregiver holding. Most recently, Airaksinen et al. (2022) conducted a validation study of body position classification in either a home or clinic testing in 4- to 19-month-olds, refining their previous method to detect moments that infants were carried by caregivers. Classification accuracy did not vary between lab and home settings, and was generally high (95\%, \emph{kappa} = .93). Although all three studies yielded promising classification accuracy, accuracy was assessed in brief (15-60 minute) sessions supervised by a researcher, leaving the open question of how well body position classification will scale to testing across an entire day of natural home life.

@@

Accordingly, the overarching goal of the current study is to test the feasibility and validity of long-form body position recording in the home during unsupervised, everyday behavior. Supervised recordings from past work (Airaksinen et al., 2022, 2020; Franchak et al., 2021), whether in the home or in the lab, let researchers set up the situation to encourage or restrict certain behaviors. Usually, caregivers are asked to play with the infant. However, across a real day, non-play activities (e.g., eating lunch in a high chair) create challenging situations for applying automated classification of body position. Will models trained on video-recorded observations at the beginning of the day generalize to predict behavior at a later time? Assessing the validity of temporally \emph{distal} periods is a crucial step to establish whether automatic classification can be used to measure body position across a day.

In the current study, we report the feasibility and validity of body position classification over the full day in the home based on 35 testing sessions from 23 infants aged 4-14 months. Participants received a custom pair of infant leggings embedded with 4 IMUs (one on each ankle and one on each hip) and a video camera to collect ground truth data about infant body position. A \emph{proximal comparison} period began when participants received the equipment and completed a guided phone call during which caregivers were asked to elicit different body positions based on prompts from the experimenter. Although not directly supervised, this period was most similar to previous recordings because it occurred during a convenient time for the infant and caregiver to play while they received instructions from the experimenter. The \textbf{first goal} of the current study was to determine the accuracy of body position classification during the proximal comparison period using this novel, semi-supervised procedure in participants' homes.

@@

After this second video recording period, we asked caregivers to keep infants wearing IMUs for the rest of the day until their regular bedtime, creating the \textbf{first real-time, full-day dataset of infant body position}. Interpreting such data required caregivers to log when infants napped, when they removed the sensor garment for diaper changes or other reasons, and when infants went to bed at the end of the day. The \textbf{third goal} of the study was to examine the quality of the full-day data. Could body position be successfully recorded over the desired period? Finally, the novel full-day dataset affords us a unique chance to ask whether the estimated time infants spent in different body positions align with past results using video and survey methods. Thus, the \textbf{fourth goal} of the current study was to determine whether full-day body position measurements conformed to expectations about age differences in body position. Based on past results (Franchak, 2019), infants should spend increasingly more time sitting and upright but less time supine over the age range tested (4 to 14 months).

@@

\leavevmode\vadjust pre{\hypertarget{ref-AdolphVereijken1998}{}}%
Adolph, K. E., Vereijken, B., \& Denny, M. A. (1998). Learning to crawl. \emph{Child Development}, \emph{69}, 1299--1312. \url{https://doi.org/10.1111/j.1467-8624.1998.tb06213.x}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Arif2015}{}}%
Arif, M., \& Kattan, A. (2015). Physical activities monitoring using wearable acceleration sensors attached to the body. \emph{{PLoS ONE}}, \emph{10}, e0130851.

\leavevmode\vadjust pre{\hypertarget{ref-ArmstrongCovington2019}{}}%
Armstrong, B., Covington, L. B., Hager, E. R., \& Black, M. M. (2019). Objective sleep and physical activity using 24-hour ankle-worn accelerometry among toddlers from low-income families. \emph{Sleep Health}, \emph{5}(5), 459--465.

\leavevmode\vadjust pre{\hypertarget{ref-Barbaro2019}{}}%
Barbaro, K. de. (2019). Automated sensing of daily activity: A new lens into development. \emph{Developmental Psychobiology}, \emph{61}(3), 444--464.

@@

\leavevmode\vadjust pre{\hypertarget{ref-BruijnsTruelove2020}{}}%
Bruijns, B. A., Truelove, S., Johnson, A. M., Gilliland, J., \& Tucker, P. (2020). Infants' and toddlers' physical activity and sedentary time as measured by accelerometry: A systematic review and meta-analysis. \emph{International Journal of Behavioral Nutrition and Physical Activity}, \emph{17}(1), 14.

@@

\leavevmode\vadjust pre{\hypertarget{ref-CliffReilly2009}{}}%
Cliff, D. P., Reilly, J. J., \& Okely, A. D. (2009). Methodological considerations in using accelerometers to assess habitual physical activity in children aged 0--5 years. \emph{Journal of Science and Medicine in Sport}, \emph{12}(5), 557--567.

@@

\leavevmode\vadjust pre{\hypertarget{ref-HagerTilton2017}{}}%
Hager, E., Tilton, N., Wang, Y., Kapur, N., Arbaiza, R., Merry, B., \& Black, M. (2017). The home environment and toddler physical activity: An ecological momentary assessment study. \emph{Pediatric Obesity}, \emph{12}(1), 1--9.

@@

\leavevmode\vadjust pre{\hypertarget{ref-LoboHall2019}{}}%
Lobo, M. A., Hall, M. L., Greenspan, B., Rohloff, P., Prosser, L. A., \& Smith, B. A. (2019). Wearables for pediatric rehabilitation: How to optimally design and use products to meet the needs of users. \emph{Physical Therapy}, \emph{99}(6), 647--657.

@@

\leavevmode\vadjust pre{\hypertarget{ref-NamPark2013}{}}%
Nam, Y., \& Park, J. W. (2013). Child activity recognition based on cooperative fusion model of a triaxial accelerometer and a barometric pressure sensor. \emph{IEEE Journal of Biomedical and Health Informatics}, \emph{17}, 420--426.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Preece2009}{}}%
Preece, S. J., Goulermas, J. Y., Kenney, L. P. J., \& Howard, D. (2009). A comparison of feature extraction methods for the classification of dynamic activities from accelerometer data. \emph{IEEE Transactions on Biomedical Engineering}, \emph{56}, 871--879.

@@

\leavevmode\vadjust pre{\hypertarget{ref-RenDing2016}{}}%
Ren, X., Ding, W., Crouter, S. E., Mu, Y., \& Xie, R. (2016). Activity recognition and intensity estimation in youth from accelerometer data aided by machine learning. \emph{Applied Intelligence}, \emph{45}(2), 512--529.

\leavevmode\vadjust pre{\hypertarget{ref-SchnellerBentsen2017}{}}%
Schneller, M. B., Bentsen, P., Nielsen, G., Brønd, J. C., Ried-Larsen, M., Mygind, E., \& Schipperijn, J. (2017). Measuring children's physical activity. \emph{Medicine \& Science in Sports \& Exercise}, \emph{49}(6), 1261--1269. \url{https://doi.org/10.1249/mss.0000000000001222}

@@

\leavevmode\vadjust pre{\hypertarget{ref-StewartNarayanan2018}{}}%
Stewart, T., Narayanan, A., Hedayatrad, L., Neville, J., Mackay, L., \& Duncan, S. (2018). A dual-accelerometer system for classifying physical activity in children and adults. \emph{Medicine and Science in Sports and Exercise}, \emph{50}(12), 2595--2602.
